---
title: "Oregon Population Forecast Program"
subtitle: "Preliminary Forecasts for Counties & UGBs"
author: "Josephine County"
institute: "Portland State University Population Research Center"
date: "December 2025"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

class: center

# Comments or Questions?

## Contact PSUPRC
Email: [askprc@pdx.edu](mailto:askprc@pdx.edu)  
Telephone: 503-725-3922


## Preliminary Population Projections
https://www.pdx.edu/population-research/population-forecasts

---

class: center

# PSUPRC Project Team

.pull-left[
**Neal Marquez**  
*Population Forecast Project Manager*

**Joshua Wilde**  
*Research Scientist*

**Gilbert Montcho**  
*Demographic and Labor Economics Analyst*

]

.pull-right[
**Ethan Sharygin**  
*Director*

**Huda Alkitkat**  
*Population Estimates Project Manager*

**David Swanson**  
*Research Associate*

**Suniva Thangaraj**  
*Program Manager*
]

---

# Josephine County Outline

- Population Overview
- Total Population
- Births
- Deaths
- Migration
- Aging
- Race & Ethnicity
- UGB Forecasts

---

# Josephine at a Glance: 2020 Census

``` {css, echo =F} 
    .pulll-left {
      float: left;
      width: 20%;
    }

    .pulll-right {
      float: right;
     width: 68%;
   }
```

``` {css, echo =F} 
    .pux-left {
      float: left;
      width: 38%;
    }

    .pux-right {
      float: right;
     width: 58%;
   }
```

```{css, echo = F}
.city table {
  font-size: 14px;     
}
```

```{r echo = FALSE, message = FALSE, warning = FALSE}
library(tidyverse)
library(plotly)
focus_county <- "Josephine"
model <- "model_39"
model_ugb <- "model_36a_constrained"

county_plots <- "../../../../model_plots/plots_" %>%
    str_c(model, ".rds") %>%
    read_rds()
ugb_plots <- "../../../../model_plots/ugb_plots_" %>%
    str_c(model_ugb, ".rds") %>%
    read_rds()
map_list <- "../../../../maps/ugb_city_compare_html/" %>% 
    str_c(focus_county, ".rds") %>%
    read_rds()
sector_plots <-  "../../../../processing_plots/sector_trends/sector_plots.rds" %>% 
    read_rds()
mig_plots <- "../../../../processing_plots/county_migration/" %>%
    str_c("county_migration.rds") %>%
    read_rds()

source("../../../../../Utilities/00_common_functions.R")

null0 <- capture.output(place_stat_df <- read_hist_data(
    county = FALSE, adjust_for_inflation = FALSE) %>%
    left_join(
        distinct(read_csv(ugb_cw_file), COUNTYID, CITYID, COUNTY, UGB),
        by = "CITYID", relationship = "many-to-many") %>% 
    filter(COUNTY == focus_county & UGB != "Metro") %>%
    filter(YEAR %in% c(1980, 2000, 2020)) %>%
    select(CITY, POP = POPULATION, HU, OVER65, OCC, EMPRATE, PPH, MHI, YEAR) %>%
    mutate(OVER65 = OVER65/POP*100, OCC = OCC/HU*100, EMPRATE = EMPRATE*100) %>%
    mutate(across(OVER65:PPH, function(x)sprintf("%.2f", x))) %>%
    mutate(across(POP:HU, function(x)prettyNum(x, ","))) %>%
    mutate(OVER65 = str_c(OVER65, "%")) %>%
    mutate(OCC = str_c(OCC, "%")) %>%
    mutate(EMPRATE = str_c(EMPRATE, "%")) %>%
    mutate(MHI = str_c("$", prettyNum(MHI, ","))) %>%
    select(
        CITY, YEAR, `Pop 65+` = OVER65, `Housing Units` = HU,
        `Housing Occupancy` = OCC, `Persons Per Household` = PPH,
        `Household Income` = MHI, `Employment Rate` = EMPRATE) %>%
    pivot_longer(-(CITY:YEAR)) %>%
    pivot_wider(names_from = YEAR) %>%
    rename(Metric = name))

cen_demog_df <- read_hist_data(OR_only = TRUE, adjust_for_inflation = FALSE)
cen_demog_df %>%
    select(-EMPRATE) %>%
    group_by(YEAR) %>%
    summarise(across(POPULATION:UNDER18, sum), .groups = "drop") %>%
    mutate(COUNTY = "Oregon") %>%
    bind_rows(cen_demog_df) %>%
    mutate(UNDER18 = round(UNDER18/POPULATION*100, 2)) %>%
    mutate(UNDER18 = str_c(sprintf("%.02f", UNDER18), "%")) %>%
    mutate(OVER65 = round(OVER65/POPULATION*100, 2)) %>%
    mutate(OVER65 = str_c(sprintf("%.02f", OVER65), "%")) %>%
    mutate(NONWHITE = round((1-(WHITE/POPULATION))*100, 2)) %>%
    mutate(NONWHITE = str_c(sprintf("%.02f", NONWHITE), "%")) %>%
    mutate(PPH = round(((POPULATION - GQ)/OCC), 2)) %>%
    mutate(PPH = str_c(
        sprintf("%.02f", PPH), " (",
        prettyNum(HU, big.mark = ","), " units)")) %>%
    mutate(POPULATION = prettyNum(POPULATION, big.mark = ",")) %>%
    filter(YEAR == 2020, COUNTY %in% c("Oregon", focus_county)) %>%
    select(
        COUNTY,
        `Total Population` = POPULATION,
        `Population Aged 0-17` = UNDER18,
        `Population Aged 65+` = OVER65,
        `Population non-White` = NONWHITE,
        `Persons per Household` = PPH) %>%
    mutate(COUNTY = fct_rev(fct_relevel(COUNTY, "Oregon"))) %>%
    arrange(COUNTY) %>%
    pivot_longer(-COUNTY, names_to = "Statistic") %>%
    pivot_wider(names_from = COUNTY, values_from = value) %>%
    knitr::kable(format = 'html')
    
```

---

# Josephine Employment Changes

```{r echo = FALSE, message = FALSE, warning = FALSE, out.height="500px", out.width="750px"}
ggplotly(sector_plots[[focus_county]], tooltip = "text")
```

---

# Josephine Migration Flows

```{r echo = FALSE, message = FALSE, warning = FALSE, out.height="500px", out.width="750px"}
ggplotly(mig_plots[[focus_county]], tooltip = "text")
```

---

# Josephine Population

.pulll-left[
Population growth is expected to stall, decline beginning after 2055.
]

.pulll-right[
```{r echo = FALSE, message = FALSE, warning = FALSE, out.height="400px"}
ggplotly(county_plots$county_pop[[focus_county]], tooltip = "text")
```
]

---

# Josephine Compositional Changes

.pulll-left[
Natural growth continues to decline slowing growth to the county despite consistent migration.
]

.pulll-right[
```{r echo = FALSE, message = FALSE, warning = FALSE, out.height="400px"}
ggplotly(county_plots$comp_change[[focus_county]], tooltip = "text")
```
]

---

# Josephine Births

.pulll-left[
Births are expected to fall as fertility rates in the county continue to decline.
]

.pulll-right[
```{r echo = FALSE, message = FALSE, warning = FALSE, out.height="400px"}
ggplotly(county_plots$births[[focus_county]], tooltip = "text")
```
]

---

# Josephine Deaths

.pulll-left[
Deaths are expected to increase as the popualtion continues to age.
]

.pulll-right[
```{r echo = FALSE, message = FALSE, warning = FALSE, out.height="400px"}
ggplotly(county_plots$deaths[[focus_county]], tooltip = "text")
```
]

---

# Josephine Life Expectancy & TFR

```{r echo = FALSE, message = FALSE, warning = FALSE, out.height="500px", out.width="750px", dpi=300}
county_plots$sum_plots[[focus_county]]
```

---

# Population Pyramids

.pulll-left[
Growth of the population 65 and older is expected to make the compostion of the county more "top-heavy".
]

.pulll-right[
```{r echo = FALSE, message = FALSE, warning = FALSE, out.height="400px"}
ggplotly(county_plots$age_structure[[focus_county]], tooltip = "text")
```
]

---

# Josephine Race and Ethnicity

.pulll-left[
Josephine is expected to continue to diversity as the White population slows in growth. 
]

.pulll-right[
```{r echo = FALSE, message = FALSE, warning = FALSE, out.height="400px"}
ggplotly(county_plots$raceN[[focus_county]], tooltip = "text")
```
]

---


# Josephine UGB Population Changes

```{r echo = FALSE, message = FALSE, warning = FALSE, out.height="500px", out.width="850px", dpi=300}
ugb_plots$group_ugb[[focus_county]]
```

---

class: city

# Josephine UGBs: Cave Junction in Context

.pux-right[
```{r echo = FALSE, message = FALSE, warning = FALSE,out.width="800px", out.height="400px", dpi=300}
ugb_plots$hist_pop_house_plot[[focus_county]]$`Cave Junction`
```
]

.pux-left[
```{r echo = FALSE, message = FALSE, warning = FALSE,out.height="450px"}
place_stat_df %>% 
    filter(CITY == "Cave Junction") %>%
    select(-CITY) %>%
    knitr::kable(format = "html")
```
]

---

# Josephine County: Cave Junction UGB Boundaries

```{r echo = FALSE, message = FALSE, warning = FALSE, out.height="450px"}
map_list$`Cave Junction`
```

---

# Cave Junction UGB Pop Forecast

```{r echo = FALSE, message = FALSE, warning = FALSE,out.width="750px", out.height="500px", dpi=300}
ugb_plots$ind_ugb_plot[[focus_county]]$`Cave Junction`
```

---

# Cave Junction UGB Pop Forecast

```{r echo = FALSE, message = FALSE, warning = FALSE,out.width="750px", out.height="500px", dpi=300}
ugb_plots$gr_compare[[focus_county]]$`Cave Junction`
```

---

class: city

# Josephine UGBs: Grants Pass in Context

.pux-right[
```{r echo = FALSE, message = FALSE, warning = FALSE,out.width="800px", out.height="400px", dpi=300}
ugb_plots$hist_pop_house_plot[[focus_county]]$`Grants Pass`
```
]

.pux-left[
```{r echo = FALSE, message = FALSE, warning = FALSE,out.height="450px"}
place_stat_df %>% 
    filter(CITY == "Grants Pass") %>%
    select(-CITY) %>%
    knitr::kable(format = "html")
```
]

---

# Josephine County: Grants Pass UGB Boundaries

```{r echo = FALSE, message = FALSE, warning = FALSE, out.height="450px"}
map_list$`Grants Pass`
```

---

# Grants Pass UGB Pop Forecast

```{r echo = FALSE, message = FALSE, warning = FALSE,out.width="750px", out.height="500px", dpi=300}
ugb_plots$ind_ugb_plot[[focus_county]]$`Grants Pass`
```

---

# Grants Pass UGB Pop Forecast

```{r echo = FALSE, message = FALSE, warning = FALSE,out.width="750px", out.height="500px", dpi=300}
ugb_plots$gr_compare[[focus_county]]$`Grants Pass`
```

---

class: center

# Comments or Questions?

## Contact PSUPRC
Email: [askprc@pdx.edu](mailto:askprc@pdx.edu)  
Telephone: 503-725-3922


## Preliminary Population Projections
https://www.pdx.edu/population-research/population-forecasts
